Enforced Invariant Confluence

### 2018-03-03 doc/paper_redux/iconfluence.tex
Fixed a couple of dangling references.
Moved figs into a separate directory.
Fixed dangling reference.

There are three ways to think about state-based \Iconfluence{}: a process-based
approach, a graph-based approach, and an expression-based approach. All three
approaches are illustrated in \figref{statebasedmodels} and are described in
more detail below.

\input{statebased_iconfluence.fig}

@@

As with state-based objects, there are three ways to think about
operation-based \Iconfluence{}: a process-based approach, a graph-based
approach, and an expression-based approach. All three approaches are
illustrated in \figref{opbasedmodels} and are described in more detail below.

\input{opbased_iconfluence.fig}

>>>>

There are three ways to think about state-based \Iconfluence{}: a process-based
approach, a graph-based approach, and an expression-based approach. All three
approaches are illustrated in \figref{StateBasedModels} and are described in
more detail below.

\input{figs/statebased_iconfluence.fig}

@@

As with state-based objects, there are three ways to think about
operation-based \Iconfluence{}: a process-based approach, a graph-based
approach, and an expression-based approach. All three approaches are
illustrated in \figref{OpBasedModels} and are described in more detail below.

\input{figs/opbased_iconfluence.fig}
